---
title: "Wrangling-Session2.1-Assignment"
author: "Lauren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dslabs)
```

Question 11: Examine the built-in dataset co2. This dataset comes with base R, not dslabs - just type co2 to access the dataset.
Is co2 tidy? Why or why not?

Question 12: Define the co2_wide object & tidy format.
```{r}
data(co2)
str(co2)
co2_wide <- data.frame(matrix(co2, ncol = 12, byrow = TRUE)) %>% 
  setNames(1:12) %>%
  mutate(year = as.character(1959:1997))
str(co2_wide)
co2_tidy <- co2_wide %>% pivot_longer(-year, names_to = "month", values_to = "co2")
co2_tidy
```

Question 13: Use co2_tidy to plot CO2 versus month with a different curve for each year:
```{r}
co2_tidy %>% ggplot(aes(as.numeric(month), co2, color = year)) + geom_line()
```

Question 14: Load the admissions dataset from dslabs, which contains college admission information for men and women across six majors, and remove the applicants percentage column. 
Which command could help you to wrangle the data into the desired format?
```{r}
library(dslabs)
data(admissions)
dat4 <- admissions %>% select(-applicants)
dat4
dat4_tidy <- pivot_wider(dat4, names_from = gender, values_from = admitted)
dat4_tidy
```

Question 15: Now use the admissions dataset to create the object tmp, which has columns major, gender, key and value.Combine the key and gender and create a new column called column_name to get a variable with the following values: admitted_men, admitted_women, applicants_men, and applicants_women. Save the new data as tmp2.
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
tmp <- admissions %>%
  pivot_longer(cols = c(admitted, applicants), names_to = "key", values_to = "value")
tmp
tmp2 <- tmp %>% unite(column_name, c(key, gender))
tmp2
```
